Age-related changes in plant growth and traits

### 2016-11-29 scripts/nutrient.Rmd
trying to bring in data on stem diameter with and without bark - equation to take mean of diameters is not working

#looking at sequential discs from stems
```{r}
wood_discs_base <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_base"))%>%
    select(individual_rep1,species,P) 
names(wood_discs_base) <- c("individual","species","P_base")

@@

```
unique(nutrient$tissue_complete)

>>>>

use <- subset(nutrient,nutrient$with_bark_diam_mm!="")

for (i in 1:length(use$individual_rep1)) {
  if (use$with_bark_diam_mm[i]=="") {
    use$with_bark_diam <- 3
    use$with_bark_diam <- mean(as.numeric(unlist(strsplit(as.character(use$with_bark_diam_mm), split = ";"))))
  } else {
    nutrient$with_bark_diam <- 4
  }
}

subset(nutrient$with_bark_diam_mm,nutrient$with_bark_diam_mm!="")
#looking at sequential discs from stems
```{r}
wood_discs_base <- nutrient %>%
    subset(tissue_complete %in% c("wood_from_base"))%>%
    select(individual_rep1,species,P) 
names(wood_discs_base) <- c("individual","species","P_base")

@@

```
names(nutrient)
